Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-07 tex/main.tex
more

\begin{definition}\rm
Let $\DDD$ be a set of function definitions for $\sfundefs{\Sigma}$. The set
$\DDD$ is \emph{total} if for every
$(\stypes{\Sigma},\, \sfuns{\Sigma} - \sfundefs{\Sigma})$-interpretations
$\I_0$, there exists a unique
$\Sigma$-interpretation $\I$ that extends $\I_0$
and for which $\I \models \DDD$.
\end{definition}

\begin{theorem}
If
$\DDD = \{ \forallf{\con{f}_1} \vec x.\; \varphi_1, \ldots, \forallf{\con{f}_n}
\vec x.\; \varphi_n \}
$ is a total set of function definitions, then it is admissible.
\end{theorem}
\begin{proofsketch}
Let $\varphi$ be a $T$-satisfiable formula closed under function expansion with
respect to $\DDD$.

We must show that the formula
$\varphi \wedge \bigwedge \Delta$ is also $T$-satisfiable.

Let $\J$ be a model of $\varphi$.

Let $\I_0$ be the restriction of $\J$ to the function symbols in $\sfuns{\Sigma} -
\sfundefs{\Sigma}$. By hypothesis, there exists a $\Sigma$-interpretation
$\I$ such that $\I \models \Delta$.

We must show that $\I$ coincides with $\J$ at the points of the functions
$\con{f}_i$ that they care about:

I.e. $\I$ is also a model of $\varphi$.
And by assumoption $I \models \Delta$, hence

>>>>

\begin{definition}\rm
Let $\DDD$ be a set of function definitions for $\sfundefs{\Sigma}$. The set
$\DDD$ is \emph{total} if for every
$(\stypes{\Sigma},\, \sfuns{\Sigma} - \sfundefs{\Sigma})$-interpretations
$\J_0$, there exists a unique
$\Sigma$-interpretation $\J$ that extends $\J_0$
and for which $\J \models \DDD$.
\end{definition}

\begin{theorem}
If
$\DDD$ is a total set of function definitions for
$\sfundefs{\Sigma} = \{\con{f}_1,\ldots,\con{f}_n\}$, then it is admissible.
\end{theorem}
\begin{proofsketch}
Let $\psi$ be a satisfiable formula closed under function expansion with
respect to $\DDD$. We show that $\psi \wedge \bigwedge \Delta$ is also
satisfiable. Let $\I$ be a model of $\psi$, and
let $\J_0$ be the restriction of $\I$ to the function symbols in $\sfuns{\Sigma} -
\sfundefs{\Sigma}$. By hypothesis, there exists a $\Sigma$-interpretation
$\J$ such that $\J \models \Delta$.

Since $\psi$ is closed under function expansion, it already constraints the
functions in $\sfundefs{\Sigma}$ recursively in as much as their interpretation
is necessary when interpreting $\psi$. Thus, any point $v$ for which
$\const{f}_i^\I(v)$ is queried when interpreting $\psi$ will have its
expected value according to its definition and hence coincide with $\J$.
And since $\psi$ does not depend on the interpretation at the other points,
$\J$ is, like $\I$, a model of $\psi$. Furthermore, $\J \models \Delta$ by
assumption. Thus, $\J \models \psi \wedge \bigwedge \Delta$.
